%%% Author: mterenui (F.M.T. C)
%%% Docs: https://github.com/xxx
%%% License: GNU General Public License v3.0
%%% This document is provided as a general template for informational purposes only and does not constitute legal advice. Permission is granted to copy, modify, and use this template for personal or commercial purposes, provided that this copyright and license notice is retained in all copies or substantial portions of the document. The author makes no representations or warranties regarding the legal validity or enforceability of this template in any jurisdiction. Users are strongly encouraged to consult a qualified legal professional before using this document.

\section{Donation}
\label{sec:donation}

\subsection{Description of Donation}

The \textbf{\textit{Donor}} hereby agrees to make a voluntary and irrevocable donation to the \textbf{\textit{Recipient}} (the “\textit{Donation}”) consisting of the following:

\vspace{0.3cm}

\noindent $\square$ \textbf{Monetary Donation:} \\
A sum of \donationAmount{} payable in one lump sum.

\vspace{0.3cm}

\noindent $\square$ \textbf{Non-Monetary Donation (Property or Goods):} \\
A detailed description of the donated property, goods, or assets, including quantity, condition, and identifying information:

\vspace{0.3cm}

\noindent
\begin{tabular}{p{4cm} p{4cm} p{4cm} p{4cm}}
\textbf{Item} & \textbf{Description} & \textbf{Quantity} & \textbf{Condition} \\ 
Item 1 & XX & XX & XX \\ 
Item 2 & XX & XX & XX \\ 
Item 3 & XX & XX & XX \\ 
\end{tabular}

\subsection{Method and Timing of Transfer}
The \textit{Donation} shall be transferred to the Recipient on or before \donationDate{} by the following method(s):

\vspace{0.3cm}

\noindent
\begin{tabular}{p{6cm} p{10cm}}
\textbf{$\square$ Cash} & \LoanRepaymentCashMethod{} \\ 
\textbf{$\square$ Bank Transfer} & \LoanRepaymentBankMethod{} \\ 
\textbf{$\square$ Check} & \LoanRepaymentCheckMethod{} \\ 
\textbf{$\square$ Physical delivery} & \LoanRepaymentCheckMethod{} \\ 
\textbf{$\square$ Other} & \LoanRepaymentOtherMethod{} \\ 
\end{tabular}

\vspace{0.3cm}

\noindent The \textit{Donation} shall be deemed complete upon receipt by the \textbf{\textit{Recipient}} or, in the case of property, upon transfer of ownership or control, as applicable.

\subsection{Valuation of Non-Monetary Donations}
For non-monetary donations:
\begin{itemize}
  \item The \textbf{\textit{Donor}} acknowledges that any stated value is provided for reference or internal purposes only.
  \item The \textbf{\textit{Recipient}} makes no representation or warranty regarding the fair market value of the donated property.
  \item Any valuation for tax purposes shall be the sole responsibility of the \textbf{\textit{Donor}}, unless otherwise required by law.
\end{itemize}

\subsection{Condition of Donated Property}
Unless otherwise expressly stated in writing, all non-monetary donations are made “\textit{as is}” and “\textit{where is},” without any warranties, express or implied, including warranties of condition, fitness for a particular purpose, or merchantability.

\subsection{Costs and Expenses}
Unless otherwise agreed in writing:
\begin{itemize}
  \item The \textbf{\textit{Donor}} shall be responsible for all costs associated with delivering or transferring the Donation to the \textbf{\textit{Recipient}}.
  \item The \textbf{\textit{Recipient}} shall be responsible for costs incurred after receipt, including storage, maintenance, or use.
\end{itemize}

\subsection{No Reversionary Interest}
Except as expressly provided in this Agreement, the \textbf{\textit{Donor}} retains no ownership, control, or reversionary interest in the Donation after it has been transferred to the \textbf{\textit{Recipient}}.

\subsection{Acknowledgment of Receipt}
The \textbf{\textit{Recipient}} agrees to acknowledge receipt of the \textit{Donation} in writing upon request, specifying the date and description of the \textit{Donation}, but not assigning or confirming a monetary value unless required by law.

%%% End of document (donation.tex)