%%% Author: mterenui (F.M.T. C)
%%% Docs: https://github.com/xxx
%%% License: GNU General Public License v3.0
%%% This document is provided as a general template for informational purposes only and does not constitute legal advice. Permission is granted to copy, modify, and use this template for personal or commercial purposes, provided that this copyright and license notice is retained in all copies or substantial portions of the document. The author makes no representations or warranties regarding the legal validity or enforceability of this template in any jurisdiction. Users are strongly encouraged to consult a qualified legal professional before using this document.

\section{Termination and Return of Donation}
\label{sec:termination}

\subsection{Termination}
This Agreement may terminate upon the earliest of the following events:
\begin{itemize}
  \item Completion of the purpose for which the \textit{Donation} was made;
  \item Mutual written agreement of the Parties; or
  \item Default or breach by either Party as set forth in this Agreement that remains uncured after written notice.
\end{itemize}

\vspace{0.3cm}

\noindent Termination of the Agreement shall not relieve the Parties of obligations accrued prior to termination.

\subsection{Conditions for Return of Donation}
In the event the \textit{Donation} cannot be used for the intended purpose, or if other conditions arise as specified below, the \textit{Donation}, or any portion thereof, may be returned to the \textbf{\textit{Donor}}:
\begin{itemize}
  \item \textbf{Restricted Donations: }If the \textit{Donation} is restricted to a specific purpose and the \textbf{\textit{Recipient}} is unable to apply it to that purpose due to legal, regulatory, or operational reasons.
  \item \textbf{Material Misuse: } If the \textit{Donation} is misapplied in a manner contrary to the terms of this Agreement.
\end{itemize}

\vspace{0.3cm}

\noindent Any return of \textit{Donation} shall comply with applicable laws and regulations regarding charitable contributions, including restrictions on tax-deductible contributions.

\subsection{Procedure for Return}
\begin{itemize}
  \item The \textbf{\textit{Recipient}} shall notify the \textbf{\textit{Donor}} in writing if the \textit{Donation} cannot be used as intended.
  \item The Parties shall agree in good faith on the amount, timing, and method of returning the \textit{Donation}.
  \item Return of non-monetary \textit{Donation} shall include transfer of ownership and any related documentation, with the property returned in substantially the same condition as received, ordinary wear and tear excepted.
  \item Any costs associated with returning the \textit{Donation} shall be borne by the \textbf{\textit{Recipient}}.
\end{itemize}

\subsection{No Obligation Beyond Return}
Upon return of the \textit{Donation} in accordance with this Agreement:
\begin{itemize}
  \item Neither Party shall have further obligations regarding the \textit{Donation}, except for any accrued responsibilities prior to termination.
  \item The \textbf{\textit{Donor}} shall have no claim for additional damages, interest, or compensation beyond the returned value of the \textit{Donation}.
\end{itemize}
%%% End of document (termination.tex)